Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-03-27 paper.qmd
Add different 2D layouts for PBMC data with different parameter choices

umap_plot_pbmc <- umap_pbmc_scaled |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.5) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + 
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm')) 
```

@@

umap_plot_pbmc 
```

>>>>

umap_plot_pbmc <- umap_pbmc_scaled |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + 
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm')) 
```

```{r}
#| warning: false
#| echo: false

umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_5_min_dist_0.01.rds")
umap_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = umap_pbmc, x = "UMAP1", y = "UMAP2"))) |>
  dplyr::rename(c("UMAP1" = "scaled_UMAP1", 
                  "UMAP2" = "scaled_UMAP2")) |>
  dplyr::mutate(ID = 1:NROW(umap_pbmc))

umap_plot_pbmc_1 <- umap_pbmc_scaled |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + 
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

```{r}
#| warning: false
#| echo: false

umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_15_min_dist_0.99.rds")
umap_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = umap_pbmc, x = "UMAP1", y = "UMAP2"))) |>
  dplyr::rename(c("UMAP1" = "scaled_UMAP1", 
                  "UMAP2" = "scaled_UMAP2")) |>
  dplyr::mutate(ID = 1:NROW(umap_pbmc))

umap_plot_pbmc_2 <- umap_pbmc_scaled |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + 
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

```{r}
#| warning: false
#| echo: false

umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_15_min_dist_0.03.rds")
umap_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = umap_pbmc, x = "UMAP1", y = "UMAP2"))) |>
  dplyr::rename(c("UMAP1" = "scaled_UMAP1", 
                  "UMAP2" = "scaled_UMAP2")) |>
  dplyr::mutate(ID = 1:NROW(umap_pbmc))

umap_plot_pbmc_3 <- umap_pbmc_scaled |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + 
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

```{r}
#| warning: false
#| echo: false

umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_84_min_dist_0.99.rds")
umap_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = umap_pbmc, x = "UMAP1", y = "UMAP2"))) |>
  dplyr::rename(c("UMAP1" = "scaled_UMAP1", 
                  "UMAP2" = "scaled_UMAP2")) |>
  dplyr::mutate(ID = 1:NROW(umap_pbmc))

umap_plot_pbmc_4 <- umap_pbmc_scaled |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + 
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

```{r}
#| warning: false
#| echo: false
tsne_pbmc <- read_rds("data/pbmc3k/pbmc_tsne_5.rds")
tsne_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = tsne_pbmc, 
                                                                 x = "tSNE1", y = "tSNE2"))) |>
  dplyr::rename(c("tSNE1" = "scaled_tSNE1", 
                  "tSNE2" = "scaled_tSNE2")) |>
  dplyr::mutate(ID = 1:NROW(tsne_pbmc))

tsne_plot_pbmc_1 <- tsne_pbmc_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + #ggtitle("(a)") +
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm')) 
```

```{r}
#| warning: false
#| echo: false
tsne_pbmc <- read_rds("data/pbmc3k/pbmc_tsne_51.rds")
tsne_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = tsne_pbmc, 
                                                                 x = "tSNE1", y = "tSNE2"))) |>
  dplyr::rename(c("tSNE1" = "scaled_tSNE1", 
                  "tSNE2" = "scaled_tSNE2")) |>
  dplyr::mutate(ID = 1:NROW(tsne_pbmc))

tsne_plot_pbmc <- tsne_pbmc_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + #ggtitle("(a)") +
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm')) 
```

```{r}
#| warning: false
#| echo: false
tsne_pbmc <- read_rds("data/pbmc3k/pbmc_tsne_92.rds")
tsne_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = tsne_pbmc, 
                                                                 x = "tSNE1", y = "tSNE2"))) |>
  dplyr::rename(c("tSNE1" = "scaled_tSNE1", 
                  "tSNE2" = "scaled_tSNE2")) |>
  dplyr::mutate(ID = 1:NROW(tsne_pbmc))

tsne_plot_pbmc_2 <- tsne_pbmc_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + #ggtitle("(a)") +
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm')) 
```

```{r}
#| warning: false
#| echo: false

phate_pbmc <- read_rds("data/pbmc3k/pbmc_phate_2.rds")
phate_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = phate_pbmc, x = "PHATE1", y = "PHATE2"))) |>
  dplyr::rename(c("PHATE1" = "scaled_PHATE1", 
                  "PHATE2" = "scaled_PHATE2")) |>
  dplyr::mutate(ID = 1:NROW(phate_pbmc))

phate_plot_pbmc_1 <- phate_pbmc_scaled |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + 
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

```{r}
#| warning: false
#| echo: false

phate_pbmc <- read_rds("data/pbmc3k/pbmc_phate_5.rds")
phate_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = phate_pbmc, x = "PHATE1", y = "PHATE2"))) |>
  dplyr::rename(c("PHATE1" = "scaled_PHATE1", 
                  "PHATE2" = "scaled_PHATE2")) |>
  dplyr::mutate(ID = 1:NROW(phate_pbmc))

phate_plot_pbmc_2 <- phate_pbmc_scaled |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + 
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

```{r}
#| warning: false
#| echo: false

phate_pbmc <- read_rds("data/pbmc3k/pbmc_phate_10.rds")
phate_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = phate_pbmc, x = "PHATE1", y = "PHATE2"))) |>
  dplyr::rename(c("PHATE1" = "scaled_PHATE1", 
                  "PHATE2" = "scaled_PHATE2")) |>
  dplyr::mutate(ID = 1:NROW(phate_pbmc))

phate_plot_pbmc_3 <- phate_pbmc_scaled |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) + 
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

```{r}
#| warning: false
#| echo: false

trimap_pbmc <- read_rds("data/pbmc3k/pbmc_trimap_12_4_3.rds")
trimap_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = trimap_pbmc, x = "TriMAP1", y = "TriMAP2"))) |>
  dplyr::rename(c("TriMAP1" = "scaled_TriMAP1",
                  "TriMAP2" = "scaled_TriMAP2")) |>
  dplyr::mutate(ID = 1:NROW(trimap_pbmc))

trimap_plot_pbmc_1 <- trimap_pbmc_scaled |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) +
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

```{r}
#| warning: false
#| echo: false

trimap_pbmc <- read_rds("data/pbmc3k/pbmc_trimap_30_4_10.rds")
trimap_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = trimap_pbmc, x = "TriMAP1", y = "TriMAP2"))) |>
  dplyr::rename(c("TriMAP1" = "scaled_TriMAP1",
                  "TriMAP2" = "scaled_TriMAP2")) |>
  dplyr::mutate(ID = 1:NROW(trimap_pbmc))

trimap_plot_pbmc_2 <- trimap_pbmc_scaled |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) +
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

```{r}
#| warning: false
#| echo: false

trimap_pbmc <- read_rds("data/pbmc3k/pbmc_trimap_5_2_2.rds")
trimap_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = trimap_pbmc, x = "TriMAP1", y = "TriMAP2"))) |>
  dplyr::rename(c("TriMAP1" = "scaled_TriMAP1",
                  "TriMAP2" = "scaled_TriMAP2")) |>
  dplyr::mutate(ID = 1:NROW(trimap_pbmc))

trimap_plot_pbmc_3 <- trimap_pbmc_scaled |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) +
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

```{r}
#| warning: false
#| echo: false

pacmap_pbmc <- read_rds("data/pbmc3k/pbmc_pacmap_10_pca_0.5_2.rds")
pacmap_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = pacmap_pbmc, x = "PaCMAP1", y = "PaCMAP2"))) |>
  dplyr::rename(c("PaCMAP1" = "scaled_PaCMAP1",
                  "PaCMAP2" = "scaled_PaCMAP2")) |>
  dplyr::mutate(ID = 1:NROW(pacmap_pbmc))

pacmap_plot_pbmc_1 <- pacmap_pbmc_scaled |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) +
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

```{r}
#| warning: false
#| echo: false

pacmap_pbmc <- read_rds("data/pbmc3k/pbmc_pacmap_30_random_0.9_5.rds")
pacmap_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = pacmap_pbmc, x = "PaCMAP1", y = "PaCMAP2"))) |>
  dplyr::rename(c("PaCMAP1" = "scaled_PaCMAP1",
                  "PaCMAP2" = "scaled_PaCMAP2")) |>
  dplyr::mutate(ID = 1:NROW(pacmap_pbmc))

pacmap_plot_pbmc_2 <- pacmap_pbmc_scaled |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) +
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

```{r}
#| warning: false
#| echo: false

pacmap_pbmc <- read_rds("data/pbmc3k/pbmc_pacmap_5_pca_0.1_1.rds")
pacmap_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = pacmap_pbmc, x = "PaCMAP1", y = "PaCMAP2"))) |>
  dplyr::rename(c("PaCMAP1" = "scaled_PaCMAP1",
                  "PaCMAP2" = "scaled_PaCMAP2")) |>
  dplyr::mutate(ID = 1:NROW(pacmap_pbmc))

pacmap_plot_pbmc_3 <- pacmap_pbmc_scaled |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) +
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

```{r}
#| warning: false
#| echo: false

pacmap_pbmc <- read_rds("data/pbmc3k/pbmc_pacmap_30_random_0.1_1.rds")
pacmap_pbmc_scaled <- as.data.frame(do.call(cbind, gen_scaled_data(data = pacmap_pbmc, x = "PaCMAP1", y = "PaCMAP2"))) |>
  dplyr::rename(c("PaCMAP1" = "scaled_PaCMAP1",
                  "PaCMAP2" = "scaled_PaCMAP2")) |>
  dplyr::mutate(ID = 1:NROW(pacmap_pbmc))

pacmap_plot_pbmc_4 <- pacmap_pbmc_scaled |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1) +
  coord_equal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold")) +
  theme_linedraw() +
  theme(legend.position = "none", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=5), #change legend title font size
        legend.text = element_text(size=4),
        legend.key.height = unit(0.25, 'cm'),
        legend.key.width = unit(0.25, 'cm'))

```

@@

umap_plot_pbmc + umap_plot_pbmc_1 + umap_plot_pbmc_2 + umap_plot_pbmc_3 + umap_plot_pbmc_4 + tsne_plot_pbmc_1 + tsne_plot_pbmc + tsne_plot_pbmc_2 + phate_plot_pbmc_1 + phate_plot_pbmc_2 + phate_plot_pbmc_3 + trimap_plot_pbmc_1 + trimap_plot_pbmc_2 + trimap_plot_pbmc_3 + pacmap_plot_pbmc_1 + pacmap_plot_pbmc_2 + pacmap_plot_pbmc_3 + pacmap_plot_pbmc_4 + plot_layout(ncol = 6)
```
